\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-07 paper.tex
Consolidate image collections
Minor clean up
Enforce latexindent
Add future work - data auction

\begin{document}
%
\title{\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}}
%
\author{
%%% Fill in name here
%\IEEEauthorblockN{
\large Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua (Vivian) Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}
%}\\

%%% Fill in school here
\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\

%%% Fill in address here
\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\

%%% Fill in city and country here
\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\

%%% Fill in email here
\IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
}

%

\maketitle              
% 50-80 words
\section{\normalsize\textbf{Abstract}}
Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

@@

\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns. We call this as a maintain period. Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discounted factor $\beta$ to depict this phenomena.

@@

\section{\normalsize\textbf{Conclusion}}

% ---- Bibliography ----
\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}

>>>>

\begin{document}
\title{\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}}
\author{
    \large Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua (Vivian) Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}

    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\

    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\

    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\

    \IEEEauthorblockA{\normalsize\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
}

\maketitle
\section*{\normalsize\textbf{Abstract}}
Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

@@

\begin{figure} \centering \includegraphics[width=3.3in]{decision_tree} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns. We call this as a maintain period. Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discounted factor $\beta$ to depict this phenomena.

@@

\section{\normalsize\textbf{Future Work}}
%Data Auction
The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there has been many auction models\cite{BigPicDataMarket} in several areas, only a few of research focus on third-party auction platform. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants and analyzing potential threats are still critical issues that need to be resolved.

% ---- Bibliography ----
\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}
